---
title: "Pathoscope Initial Analysis"
author: "Nate Olson"
date: "12/16/2014"
output: html_document
---
Objective:
Approach:


### Loading Data
```{r}
library(knitr)
library(ggplot2)
source('gather_pathoscope.R')
df <- join(pathoDF, sampleDF)
```

## Top matches
The organisms with the top matches were all *Salmonella enterica subspecies enterica*, and the porportion of reads assigned to the top matches was statistically similiar for all replicates (library, and vials).  
```{r, fig.height=10}
ggplot(df[df$Final_Guess > 0.001,]) + geom_boxplot(aes(y = Final_Guess, x = plat, color = Genome)) + scale_y_log10() +  facet_wrap(~plat, scale = "free_x") + theme_bw()
```

Top proportion of assignments for all datasets were correct to the subspecies level.  LT2 was the top portion for all PGM datasets but not for MiSeq.

### Top Assignment Repeatability
```{r, fig.height=10}
ggplot(df[df$Final_Guess > 0.1,]) + geom_jitter(aes(y = Final_Guess, x = plat, color = Genome))  + theme_bw() + theme(legend.position = "bottom", legend.direction = "vertical")
```

The top hits for the replicate datasets for the individual platformsthe two datasets statistically similar.
```{r}
for(i in c("MiSeq","PGM")){
  print(i)
  print(t.test(df$Final_Guess[df$Final_Guess > 0.1 & df$plat == i]))
}
```

### Analysis of contaminants
Defining contaminants as non-*Salmonella*, sequence purity and genomic sturcture analysis are better suited for evaluating the presence of closely related species within the material.
```{r}
df$Contam <- !(grepl("Salmonella", df$Genome))
```

```{r}
ggplot(df[df$Contam == TRUE,]) + geom_density(aes(x = Final_Guess), alpha = 0.25) + geom_rug(aes(x = Final_Guess)) + facet_wrap(~plat) + geom_vline(aes(xintercept = 1), color = "blue") + scale_x_log10() + theme_bw()
```

Blue vertical line, at 1 to serve as a reference point.

### Contaminant Summary
```{r}
df_contam <- ddply(df[df$Contam == TRUE,],.variables = .(Genome, plat),summarize, median=median(Final_Guess), max=max(Final_Guess),min=min(Final_Guess)) %>% arrange(desc(median))
```
```{r,echo=FALSE,results='asis'}
kable(df_contam[df_contam$median > 1e-10,],digits = 10, format='html')
```

Frequency a specific contaminant was observed in a dataset
```{r}
ggplot(df[df$Contam == TRUE & df$Genome %in% df_contam$Genome[df_contam$median > 1e-10],]) + geom_raster(aes(x = sampleID, y = Genome, Fill=Final_Best_Hit_Read_Numbers)) + facet_wrap(~plat, scale= "free_x")
```

Need to filter out Genomes only present in one dataset and order by number of replicates present

### Summary by org
```{r}
df_summary <- ddply(df,.variables = .(Genome, plat),summarize, median=median(Final_Guess), max=max(Final_Guess),min=min(Final_Guess)) %>% arrange(desc(median))
```

```{r,echo=FALSE,results='asis'}
kable(df_summary, format='html')
```

