---
title: "Consensus Base Analysis V1"
author: "Nate Olson"
date: "01/20/2015"
output:
  html_document:
    keep_md: yes
---

```{r, echo=FALSE, message=FALSE, warning=FALSE}
library(dplyr)
library(ggplot2)
library(ggvis)
library(knitr)
```

## Loading data
```{r}
vcf_db <- src_sqlite("../../../data/RM8375/RM8375-v01.sqlite", create = TRUE)
plat_pur <- tbl(vcf_db, "pur_join") %>% collect()
```

Note that the pgm but not the miseq is summarized by run

## Platform Pooled Purity distributions
### PGM
```{r, message=FALSE}
plat_pur %>%
  ggvis(~plat2) %>%
  layer_histograms() %>%
  add_axis("x", title = "High Quality Base Purity")
```

### Purity less than 0.98
```{r, message=FALSE}
plat_pur %>% filter(plat2 < 0.98) %>%
  ggvis(~plat2) %>%
  layer_histograms() %>%
  add_axis("x", title = "High Quality Base Purity")
```

### MiSeq
```{r, message=FALSE}
plat_pur %>%
  ggvis(~plat1) %>%
  layer_histograms() %>%
  add_axis("x", title = "High Quality Base Purity") 
```

### Purity less than 0.98
```{r, message=FALSE}
plat_pur %>% filter(plat1 < 0.98) %>%
  ggvis(~plat1) %>%
  layer_histograms() %>%
  add_axis("x", title = "High Quality Base Purity")
```

### Purity Scatter Plot
```{r}
plat_pur %>%
  filter(plat1 < 0.98 | plat2 < 0.98) %>%
  ggvis(x = ~plat1, y = ~plat2) %>%
  layer_points(fill = ~CHROM) %>%
  add_axis("x", title = "MiSeq") %>%
  add_axis("y", title = "PGM")
```

Table listing positions with purity values less than 0.98 on both platforms
```{r}
low_conf <- plat_pur %>% filter(plat1 < 0.98, plat2 < 0.98)
kable(low_conf)
```


```{r, echo=FALSE}
#Basic Purity Based Conf Labels
#low_conf <- mutate(low_conf, conf="lc") %>% select(CHROM, POS, conf)
# apply_conf <- function(tbl_name, conf_table){
#   tbl_name  %>% right_join(conf_table) %>% 
#                 mutate(conf = ifelse(conf != "lc","hc","hc"))
# }
```


### Per sample analysis
```{r}
pgm_pur <- tbl(vcf_db, "pur_pgm") %>% select(CHROM, POS, SAMPLE, Pur) %>% collect()
miseq_pur <- tbl(vcf_db, "pur_miseq")  %>% select(CHROM, POS, SAMPLE, Pur) %>% collect()
```


```{r, echo=FALSE}
# Applying basic conf labels
#pgm_pur <- apply_conf(pgm_pur, low_conf) - slow skipping for now
#miseq_pur <- apply_conf(miseq_pur, low_conf)
```

#### PGM by Sample
##### Purity less than 0.98
```{r, message=FALSE}
ggplot(pgm_pur[pgm_pur$Pur < 0.98,]) + geom_histogram(aes(x = Pur)) + facet_wrap(~SAMPLE) + theme_bw()
```

##### Purity less than 0.90
```{r, message=FALSE}
ggplot(pgm_pur[pgm_pur$Pur < 0.90,]) + geom_histogram(aes(x = Pur)) + facet_wrap(~SAMPLE) + theme_bw()
```

### MiSeq by Sample
##### Purity less than 0.98
```{r, message=FALSE}
ggplot(miseq_pur[miseq_pur$Pur < 0.98,]) + geom_histogram(aes(x = Pur)) + facet_wrap(~SAMPLE) + theme_bw()
```

##### Purity less than 0.90
```{r, message=FALSE}
ggplot(miseq_pur[miseq_pur$Pur < 0.90,]) + geom_histogram(aes(x = Pur)) + facet_wrap(~SAMPLE) + theme_bw()
```


## Session Info
```{r}
sessionInfo()
```




